Bird beak's elaboration and innovation

### 2023-06-02 Analysis/06-Figure_with_correlations.Rmd
Volume + pp for Gustova and Travis

## Correlation fable
pdf(width = 5, height = 9, file = "../Manuscript/Figures/correlations_fable_orders.pdf")
load("../Data/Processed/tip_colours_orders.rda")
orders_col <- c(tip_colours_orders, "phylogeny" = "grey")
orders_col[] <- "black"
par(mar = c(5, 8, 4, 0) + 0.1, bty = "n") # c(bottom, left, top, right)
plot.cor.scores(cor_macro_orders, col = orders_col,
                y.axis = TRUE, plot.phylo = FALSE,
                show.phylo = FALSE, xlim = c(-0.5, 1),
                main = "Species projected onto\ntheir orders' major axes") 
dev.off()
```

>>>>

## Correlation fable
pdf(width = 5, height = 9, file = "../Manuscript/Figures/correlations_fable_orders.pdf")
load("../Data/Processed/tip_colours_orders.rda")
orders_col <- c(tip_colours_orders, "phylogeny" = "grey")
orders_col[] <- "black"
par(mar = c(5, 8, 4, 0) + 0.1, bty = "n") # c(bottom, left, top, right)
plot.cor.scores(cor_macro_orders, col = orders_col,
                y.axis = TRUE, plot.phylo = FALSE,
                show.phylo = FALSE, xlim = c(-0.5, 1),
                main = "") 
dev.off()
```
